\begin{thebibliography}{9}
\addcontentsline{toc}{section}{References}

\bibitem{bridson}
  R. Bridson,
  \emph{Fluid Simulations for Computer Graphics.}
  1st Edition,
  2008.

\bibitem{zhu}
  Y. Zhu and R. Bridson,
  \emph{Animating Sand as a Fluid.}
  2005.

\bibitem{mueller}
  M. Mueller
  \emph{A Multigrid Fluid Pressure Solver Handling Separating Solid Boundary Conditions.}
  2011.

\bibitem{zhao}
  H. Zhao, 
  \emph{A Fast Sweeping Method for Eikonal Equation.}
  2005.

\bibitem{stam}
  J. Stam
  \emph{Stable Fluids.}
  1999.

\bibitem{fosterfed}
  N. Foster and R. Fedkiw
  \emph{Practical Animation of Liquids.}
  2001.

\bibitem{batty}
  C. Batty, F.Bertails and R. Bridson
  \emph{A Fast Variational Framework for Accurate Solid-Fluid Coupling}
  2007.

\bibitem{enright}
  D. Enright, S. Marschner and R. Fedkiw
  \emph{Animation and Rendering of Complex Water Surfaces.}
  2002.

\bibitem{harlow}
  F. H. Harlow 
  \emph{The Particle-in-Cell Method for Numerical Solution of Problems in Fluid Dynamics.}
  1963.

\bibitem{osher}
  S. Osher and R. Fedkiw
  \emph{Level Set Methods and Dynamic Implicit Surfaces.}
  2002.

\bibitem{chorin}
  A.J Chorin
  \emph{Numerical Solution to the Navier Stokes equations}
  1968.

\bibitem{sph}
 J.J Monaghan
 \emph{Smoothed particle hydrodynamocs.}
 1992.

\bibitem{desbrun}
  M. Desbrun and M.P Cani
  \emph {Smoothed particles: A new paradigm for animating highly deformable bodies.}
  1996.

\bibitem{metaxas}
  N. Foster and D. Metaxas
  \emph{Realistic animation of liquids.}
  1996.

\bibitem{jeong}
  W. K Jeong and T. Whitaker
  \emph{A fast eikonal equation solver for parallel systems.}
  2007.

\end{thebibliography}
