To guarantee that the velocity field is divergence-free we need to solve the pressure equations. This step is often called the projection step. We are going to use an approach introduced by Alexandre Chorin introduced \cite{chorin}. The key is to split the Euler fluid equations into two steps and solve them sequentially. In the first step we solve for the intermediate velocity field $\vec{u}^*$. This vector field is not divergence-free but we use it as an input to the second step of the splitting. We will set up the pressure equations later on in such way that removing the pressure gradient $\nabla p$ from the intermediate $\vec{u}^*$ will make $\vec{u}^{n+1}$ divergence-free.

\begin{equation}
\vec{u}^{n+1} = \vec{u}^* - \frac{\Delta t}{\rho} \nabla p
\label{pressuredivfreeeq}
\end{equation}
\noindent
If we rearrange Equation \ref{pressuredivfreeeq}, we get a substitution for the pressure term in the Euler fluid equations described in Equation \ref{eulereq}.

\begin{equation}
\frac{\vec{u}^{n+1} - \vec{u}^*}{\Delta t}= - \frac{1}{\rho} \nabla p
\label{pressuredivfreeeqsub}
\end{equation}
\noindent
If we approximate $\frac{\partial \vec{u}}{\partial t}$ with $\frac{\vec{u}^{n+1} - \vec{u}^{n}}{\Delta t}$, we can rewrite Equation \ref {eulereq} to

\begin{equation}
\begin{split}
\frac{\partial \vec{u}}{\partial t}  &= -\vec{u} \cdot \nabla \vec{u} - \frac{1}{\rho}\nabla p + \vec{f}\\
\frac{\vec{u}^{n+1} - \vec{u}^{n}}{\Delta t}  &= - \vec{u} \cdot \nabla \vec{u} + \frac{\vec{u}^{n+1} - \vec{u}^*}{\Delta t} + \vec{f} \\
\vec{u}^* & = \vec{u}^n - \Delta t(\vec{u} \cdot \nabla \vec{u}) + \Delta t\vec{f}
\end{split}
\end{equation}
\noindent
In our hybrid FLIP simulation, getting the intermediate velocity field  $\vec{u}^*$ each step is easy where the Lagrangian particle update gives the use the advection terms. Applying the integrated external forces $\vec{g}$ over timestep $\Delta t$ is trivial. The challenging part of the pressure solving step is to set up the pressure equations that enforces an incompressible fluid.
